Parallel multi-objective optimization using co-evolutionary islands and search space overlapping

### 2016-11-18 hpmoon-hpca.tex
Fixed pseudocodefor issue #6
Changed format to FGCS

% sage_latex_guidelines.tex V1.01, 11 June 2015

%\documentclass[Afour,sagev,times]{sagej}
\documentclass[Crown,sagev,times,doublespace]{sagej}

\usepackage{moreverb,url,color}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage[colorlinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlcolor=red]{hyperref}

\newcommand\BibTeX{{\rmfamily B\kern-.05em \textsc{i\kern-.025em b}\kern-.08em
T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\def\volumeyear{2016}

@@

%\runninghead{Garc\'ia-S\'anchez et al.}
\runninghead{anonymous}
\title{Parallel multi-objective optimization using co-evolutionary
  islands and search space overlapping}
% Why are you mixing caps and non-caps? - JJ Pablo: fixed

%\author{Pablo Garc\'ia-S\'anchez, Julio Ortega, Jes\'us Gonz\'alez, \\Pedro Angel Castillo and Juan Juli\'an Merelo\affilnum{1}}
\author{ANONYMOUS FOR BLIND REVIEW \affilnum{1}}
\affiliation{\affilnum{1} ANONYMOUS FOR BLIND REVIEW}
%\affiliation{\affilnum{1}Dept. of Computer Architecture and Computer Technology, University of Granada, Spain}

%\corrauth{ANONYMOUS FOR BLIND REVIEW.}

%\email{pablogarcia@ugr.es}
\email{anonymous}

\begin{abstract}
Multi-objective optimization methods have gained interest in the last
years because the performance they can achieve solving real-world
problems. 
% You can safely supress the sentence above - JJ
Many of these problems usually require a high-dimensional
decision space, and multi-objective Evolutionary Algorithms have been
% random capitalization strikes back - JJ
successfully used in the past. 
% Another useless sentence - JJ
Due to the large computational cost
these algorithms require, different parallelization and distribution
methods have been proposed, with different parallel and distributed
computer architectures to cope with them. One of the most extended
methods are the distributed co-evolutionary algorithms, where each
processor deals only with a part of the decision space, that is, the
individuals belonging to the same sub-population (island) explore the
same subset of decision variables.
%After explaining the method, you should say why it might work - JJ

@@

\keywords{Multi-objective algorithms, NSGA-II, Island model, distributed evolutionary algorithms, coevolution}

\maketitle

@@

The rest of the paper is organized as follows: after a background in parallelization in MOEAs, 
the compared algorithms and the used methodology are presented. %PABLO: no puedo usar \ref{sec:met} porque la plantilla de esta revista no lo coge :/ (y además no tienen número)
Then, the results of the experiments are shown, followed by conclusions and suggestions for future work lines.

@@

\textcolor{red}{Pseudo-code of the proposed algorithms is described in Algorithm \ref{fig:pseudo}.}

@@

\begin{algorithmic}
\STATE \textit{//In each island $i$}
\STATE population $\gets$ initialisePopulation()
\STATE \textit{//Select which part modify in this island $i$}
\STATE section $\gets$ getComponentsToModify($i$)
\WHILE {stopping criterion not met}
    \STATE parents $\gets$ nsgaSelection(population)
    \FORALL{each 2 chromosome in parents}
    	\STATE \textit{//Crossovers only the part for island $i$}
    	\STATE children  $\gets$ crossover(parents,section)
    	\STATE offspring $\gets$ offspring + children
    \ENDFOR
    \FORALL{chromosome in offspring}
    	\IF {mutationProb $>$ random()}
    		\STATE \textit{//Mutates only the part for island $i$}
    		\STATE chromosome $\gets$ mutation(chromosome,section)
    		\STATE offspring $\gets$ chromosome + offspring
    	\ENDIF
    \ENDFOR
    \STATE population $\gets$ population + offspring

@@

\subsection{Benchmark problems}
\textcolor{red}{The first part of the experiments...}

@@

\subsection{Real problem}
\textcolor{red}{A real problem has also been used.}

%Surprisingly, the average
%number of solutions of PFs per island in the baseline configuration is significantly
%higher in some configurations (mostly with 128 islands), but their
%combination in the final PF never attains higher values than Disjoint
%and Overlapping methods.

%configurations, with respect to the baseline.  Paying attention to the disjoint and
%overlapping methods, only when using 8 islands the disjoint method
%always attain better metrics, and even more times with the 2048 chromosome
%length. This can be explained because only 1/8 of the individual is
%changed in each island, while in the overlapping, 3/8 of the island
%may be more similar to the baseline configuration. 
%

@@

\begin{acks}
ANONYMOUS
%This work has been partially funded by projects TIN2014-56494-C4-3-P y TIN2015-67020-P (Spanish Ministry of Economy and Competitivity), PROY-PP2015-06 (Plan Propio 2015 UGR),  and  MSTR (PRY142/14, Fundaci\'on P\'ublica Andaluza Centro de Estudios Andaluces en la IX Convocatoria de Proyectos de Investigaci\'on).
\end{acks}

\bibliographystyle{SageV}

>>>>

%\affiliation{\affilnum{1}Dept. of Computer Architecture and Computer Technology, University of Granada, Spain}

\documentclass[preprint]{elsarticle}
\usepackage[latin1]{inputenc}
\usepackage[english]{babel}
\usepackage{moreverb,url,color}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{color}
\usepackage{url}
\usepackage[colorlinks,bookmarksopen,bookmarksnumbered,citecolor=red,urlcolor=red]{hyperref}

@@

\begin{frontmatter}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   TITLE   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Parallel multi-objective optimization using co-evolutionary
  islands and search space overlapping}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   AUTHORS   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\author{P. Garc\'ia-S\'anchez$^1$, J. Ortega$^2$, J. Gonz\'alez$^2$, P. A. Castillo$^2$ and J.J. Merelo$^2$}
\ead{pablo.garciasanchez@uca.es, \{jortega, jgonzalez, pacv, jmerelo\}@ugr.es}
\address{
$^1$ Department of Computer Science and Engineering. ESI. University of C\'adiz, Spain\\
$^2$ Department of Computer Architecture and Computer Technology.\\ ETSIIT - CITIC. University of Granada, Spain\\
}

\begin{abstract}
Multi-objective optimization methods have gained interest in the last
years because the performance they can achieve solving real-world
problems. 
Many of these problems usually require a high-dimensional
decision space, and multi-objective Evolutionary Algorithms have been
successfully used in the past. 
Due to the large computational cost
these algorithms require, different parallelization and distribution
methods have been proposed, with different parallel and distributed
computer architectures to cope with them. One of the most extended
methods are the distributed co-evolutionary algorithms, where each
processor deals only with a part of the decision space, that is, the
individuals belonging to the same sub-population (island) explore the
same subset of decision variables.
%After explaining the method, you should say why it might work - JJ

@@

\begin{keyword}
Multi-objective algorithms \sep NSGA-II \sep Island model \sep distributed evolutionary algorithms \sep coevolution
\end{keyword}

\end{frontmatter}

@@

The rest of the paper is organized as follows: after a background in parallelization in MOEAs, 
the compared algorithms and the used methodology are presented in Section \ref{sec:coevo}. %PABLO: no puedo usar \ref{sec:met} porque la plantilla de esta revista no lo coge :/ (y además no tienen número)
Then, the results of the experiments are shown (Section \ref{sec:res}), followed by conclusions and suggestions for future work lines.

@@

Pseudo-code of the proposed algorithms is described in Algorithm \ref{fig:pseudo}.

@@

\begin{algorithmic}
\STATE \textit{//In each island $i$}
\STATE population $\gets$ initialisePopulation()
\STATE \textit{//Select which part modify in this island $i$}
\STATE section $\gets$ getComponentsToModify($i$)
\IF {type = Baseline}
	\STATE $c=P/2$
\ELSIF {type = Disjoint}
	\STATE $c=0$
\ELSIF {type = Overlapping}
	\STATE $c=1$
\ELSIF {type = Adaptive}
	\STATE $c=round(0.2*P-1)/2$
\ENDIF

\WHILE {stopping criterion not met}
    \STATE parents $\gets$ nsgaSelection(population)
    \FORALL{each 2 chromosome in parents}
    	\STATE \textit{//Crossovers only the part for island $i$ (c components left and right)}
    	\STATE children  $\gets$ crossover(parentA[i-c:i+c],parentB[i-c:i+c])
    	\STATE offspring $\gets$ offspring + children
    \ENDFOR
    \FORALL{chromosome in offspring}
    	\IF {mutationProb $>$ random()}
    		\STATE \textit{//Mutates only the part for island $i$}
    		\STATE chromosome $\gets$ mutation(chromosome[i-c:i+c])
    		\STATE offspring $\gets$ chromosome + offspring
    	\ENDIF
    \ENDFOR
    \STATE population $\gets$ population + offspring

@@

%\subsection{Benchmark problems}

@@

%%%%REAL PROBLEM
%\subsection{Real problem benchmark: Unsupervised Feature Selection}
%\textcolor{red}{A real problem has also been used to BLABLABLA. In this case, the problem used to solve is the unsupervised feature selection. A dataset formed by EEG signals from Brain Computer Interface (BCI) is used as a benchmark \cite{Kimovski15Parallel}, due to the required high computational cost and chromosome length. Individuals in this case are binary vectors indicating if a specific feature is selected or not. To evaluate a set of features different clustering validation indexes (CVIs) can be used.}

%\textcolor{red}{In this case, the two objectives to compare the three methods are the inter-cluster separation ($f1$) and the intra-cluster separation ($f2$). To obtain this measures, and after applying the projection to the dataset, a method based in the one presented  \cite{Kimovski15Parallel} is applied. Starting with a random value of the projection, the distance to the closer one is stored, and so on. After ordering these distances from lower to higher, we consider the intra-cluster distance ($f1$) as the one in the position 1/4 of the list, while the inter-cluster ($f2$) distance is in the position 3/4. The intra-cluster distance objective needs to be minimized, while the inter-cluster is maximized. Figure \ref{fig:cvis} explains this method using a extremely simplified example. Note that the goal of this paper is not obtain better CVI values than other methods, but to study the different overlapping schemes in parallel MOEAs.}

%\begin{figure}
%\centering
%\includegraphics[width=10cm]{clusterCVI.pdf}
%\caption{\textcolor{red}{Method to calculate the two objectives for the Feature Selection problem. Starting from a random $d$ point of the projection of the features, the distance to the closer point is calculated iteratively. After ordering these distances, the one in the position 1/4 (a) is considered the intra-cluster distance, while the one in position 3/4 (b) is considered the inter-cluster one.}}
%\label{fig:cvis}
%\end{figure}

%\textcolor{red}{The Dataset used is ... Due to the high computational cost required for the fitness function, the running time for each run has been set to 4 hours, with two generations before sending the individual to another random island. Table \ref{tab:parametersBCI} summarizes the specific parameters for this experiment (the rest of the parameters are the same than the previous experiment, shown in Table \ref{tab:parameters} ). As there is no optimal PF known for this problem, we have used the paretos obtained from all runs to obtain the optimal PF to apply the IGD quality metric.}

%\textcolor{red}{
%\begin{table*}
%\begin{center}
%\begin{tabular}{|c|c|}
%\hline
%{\em Parameter Name} & {\em Value} \\ \hline
%Number of islands ($P$) & 8, 32 and 128 \\ \hline
%Chromosome size ($L$) & 3600 \\ \hline
%Crossover type & One-point \\ \hline
%Mutation  type & flip\\ \hline
%Generations between migration & 2 \\ \hline
%Runs per configuration & 10 \\ \hline
%\end{tabular}
%\caption{\textcolor{red}{Parameters and operators used in the experiments for Feature Selection problem (the rest of the parameters are the ones described in Table \ref{tab:parameters}).}}
%\label{tab:parametersBCI}
%\end{center}
%\end{table*}
%}

@@

\section*{Acknowledgements}
ANONYMOUS
%This work has been partially funded by projects TIN2014-56494-C4-3-P y TIN2015-67020-P (Spanish Ministry of Economy and Competitivity), PROY-PP2015-06 (Plan Propio 2015 UGR),  and  MSTR (PRY142/14, Fundaci\'on P\'ublica Andaluza Centro de Estudios Andaluces en la IX Convocatoria de Proyectos de Investigaci\'on).

\bibliographystyle{elsarticle-num}
